### 2017-07-07 README.Rmd
update readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/benmarwick/olympicdamboundaries/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/olympicdamboundaries.png?branch=master)](https://travis-ci.org/benmarwick/olympicdamboundaries) 
[![Circle CI](https://circleci.com/gh/benmarwick/olympicdamboundaries.svg?style=shield&circle-token=:circle-token)](https://circleci.com/gh/benmarwick/olympicdamboundaries)
[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

## Research compendium for a report on xxxx

@@

Marwick, B,  xxxxx

@@

This repository is our research compendium for our analysis of xxxx. The compendium contains all code, and text associated with the publication (data are not included for reasons explained in the manuscript). The `Rmd` files in the `analysis/paper/` directory contain details of how all the analyses reported in the paper were conducted, as well as instructions on how to rerun the analysis to reproduce the results. The `data/` directory in the `analysis/` directory contains all the raw data.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Research compendium for a report on Landform boundary effects on Holocene forager landscape use in arid South Australia

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/benmarwick/olympicdamboundaries/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![Travis-CI Build Status](https://travis-ci.org/benmarwick/olympicdamboundaries.png?branch=master)](https://travis-ci.org/benmarwick/olympicdamboundaries) 
[![Circle CI](https://circleci.com/gh/benmarwick/olympicdamboundaries.svg?style=shield&circle-token=:circle-token)](https://circleci.com/gh/benmarwick/olympicdamboundaries)
[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

@@

> Marwick, B, P. Hiscock, M. Sullivan, P. Hughes. 2017. Landform boundary effects on Holocene forager landscape use in arid South Australia. _Journal of Archaeological Science: Reports_ http://dx.doi.org/10.1016/j.jasrep.2017.07.004

@@

This repository is our research compendium for our analysis of Landform boundary effects on Holocene forager landscape use in arid South Australia. The compendium contains all code, and text associated with the publication (data are not included for reasons explained in the manuscript). The `Rmd` files in the `analysis/paper/` directory contain details of how all the analyses reported in the paper were conducted, as well as instructions on how to rerun the analysis to reproduce the results. The `data/` directory in the `analysis/` directory contains all the raw data.
